Region-Network Hierarchical Sparsity Priors for\\ High-Dimensional Inference in Brain Imaging

### 2016-02-03 paper/icml2016/example_paper.tex
figure* environments
ICMLize the paper

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2016}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2016}

@@

\twocolumn[
\icmltitle{Submission and Formatting Instructions for \\ 
           International Conference on Machine Learning (ICML 2016)}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2016
% package.
\icmlauthor{Your Name}{email@yourdomain.edu}
\icmladdress{Your Fantastic Institute,
            314159 Pi St., Palo Alto, CA 94306 USA}
\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
\icmladdress{Their Fantastic Institute,
            27182 Exp St., Toronto, ON M6H 2T1 CANADA}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{boring formatting information, machine learning, ICML}

@@

\textbf{\\keywords}:
Sparsity-inducing norms, hierarchical tree sparsity,
numerical optimization,
systems neuroscience,
functional specialization, functional integration

@@

\begin{table}[h]
  \resizebox{0.98\textwidth}{!}{%
  \begin{tabular}{l|l|l}
    \hline
  {\bf Cognitive Task} & {\bf Stimuli}                         & {\bf Instruction for participants}                                                \\ \hline
  1 Reward             & \multirow{2}{*}{Card game}            & \multirow{2}{*}{Guess the number of a mystery card for gain/loss of money}        \\ \cline{1-1}
  2 Punish             &                                       &                                                                                   \\ \hline
  3 Shapes             & Shape pictures                        & Decide which of two shapes matches another shape geometrically                    \\ \hline
  4 Faces              & Face pictures                         & Decide which of two faces matches another face emotionally                        \\ \hline
  5 Random             & \multirow{2}{*}{Videos with objects}  & \multirow{2}{*}{Decide whether the objects act randomly or intentionally} \\ \cline{1-1}
  6 Theory of mind     &                                       &                                                                                   \\ \hline
  7 Mathematics        & Spoken numbers                        & Complete addition and subtraction problems                                        \\ \hline
  8 Language           & Auditory stories                      & Choose answer about the topic of the story                                        \\ \hline
  9 Tongue movement    & \multirow{3}{*}{Visual cues}          & Move tongue                                                                       \\ \cline{1-1} \cline{3-3} 
  10 Food movement     &                                       & Squeezing of the left or right toe                                                \\ \cline{1-1} \cline{3-3} 
  11 Hand movement     &                                       & Tapping of the left or right finger                                               \\ \hline
  12 Matching          & \multirow{2}{*}{Shapes with textures} & Decide whether two objects match in shape or texture                             \\ \cline{1-1} \cline{3-3} 
  13 Relations         &                                       & Decide whether object pairs differ both along either shape or texture             \\ \hline
  14 View Bodies       & Pictures                              & Passive watching                                                                   \\ \hline
  15 View Faces        & Pictures                              & Passive watching                                                                   \\ \hline
  16 View Places       & Pictures                              & Passive watching                                                                   \\ \hline
  17 View Tools        & Pictures                              & Passive watching                                                                   \\ \hline
  18 Two-Back          & Various pictures                      & Indicate whether current stimulus is the same as two items earlier                \\ \hline
  \end{tabular}
}
\vspace{-0.2cm}
\caption{\textbf{Description of psychological tasks to predict.}}
\label{table_tasks}
\end{table}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{../figures/reg_net_prior_colin.pdf}
\end{centering}
\vspace{-0.6cm}
\caption{\textbf{Building blocks of the region-network tree.}
Depicts neurobiological priors introduced into the classification problem 
by hierarchical structured sparsity.
\textit{Left:} Continuous, partially overlapping brain network priors
(\textit{hot-colored}, taken from \cite{smith2009})
accommodate the functional integration
perspective of brain organization.
\textit{Right:} Discrete, non-overlapping brain region priors
(\textit{single-colored}, taken from \cite{crad12})
accommodate the functional segregation perspective.
\textit{Middle:} These two types of predefined voxel groups are incorporated
into hierarchical priors of parent networks with their
descending region nodes.
\textit{Top to bottom:} Four examplary region-network priors
are shown, including
the early cortex that processes
visual and sound information from the environment,
a well-known attentional circuit in the left brain hemisphere,
and
the cerebellum that is involved in motor behavior.
}
\label{fig_priors}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
\end{centering}
\vspace{-0.6cm}
\caption{\textbf{Model performance across sparsity priors.}
Compares the performance of logistic regression estimators
with 4 different structured and unstructered sparsity terms
in classifying neural activity from 18 psychological tasks.
The class-wise precision and recall metrics
were obtained on the same test set.
%
Unstructured $\ell_1$-penalized logistic regression (\textit{upper left})
imposed a minimum of relevant brain voxels without
assuming special structure.
Structured $\ell_1/\ell_2$-block norm with additional $\ell_1$ term
(\textit{lower left})
imposed region compartments, but naive to network structure.
Structured trace-norm penalization (\textit{lower right})
imposed low-rank structure
with sparsity of network patterns, but naive to region structure.
Structured $\ell_1/\ell_2$-block-norm with a hierarchy of
both region and network priors (\textit{upper right})
exhibited the best out-of-sample performance.
%
A priori knowledge of both region and network neighborhoods
was hence most beneficial for predicting psychological tasks from
brain maps.
}
\label{fig_sparsities}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{../figures/dataratio_trans.pdf}
\end{centering}
\vspace{-0.6cm}
\caption{\textbf{Naive versus informed sparse model selection
across training set sizes.}
Ordinary $\ell_1$-penalized logistic regression
(\textit{upper row})
is compared
to hierarchical-tree-penalized logistic regression
(\textit{lower row})
with increasing fraction
of the available training data (\textit{left to right columns}).
For one example (i.e., ``View tools'') from 18 psychological tasks,
unthresholded axial maps of model weights
are shown for comparison against
the sample average of that class
(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
The out-of-sample accuracies for predicting all 18 psychological tasks
is given in percent.
%
In the data-scarce scenario,
typical for brain imaging,
hierarchical tree sparsity achieves much
better support recovery with the biggest difference
in model performance.
%
In the data-rich scenario,
neurobiologically informed logistic regression
profits more from the available information quantities than
neurobiologically naive logistic regression.
}
\label{fig_dataratio}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{../figures/reg_net_ratio_colin.pdf}
\end{centering}
\vspace{-0.6cm}
\caption{\textbf{Support recovery as a function of
region and network emphasis.}
The relative impact of the region and network priors
on model selection
is systematically varied against each other.
This region-network ratio (\textit{upper fractions}) weighted voxel groups
to priviledge sparse models in function space
that acknowledge known brain region neighborhoods
(\textit{left columns}) or
known brain networks neighborhoods
(\textit{right columns}).
Among the 18 classes, the model weights are shown for the psychological
tasks (\textit{from top to bottom}): tongue movement, listening stories,
taking somebody else's perspective (ToM, "theory of mind"),
as well as
viewing locations and tools.
The 18-class out-of-sample accuracy is indicated
on the \textit{bottom} and
the class-wise mean neural activty
(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
%
Different emphasis on regions versus networks
in hierarchical structured sparsity can
yield comparable model performance.
%
Favoring region versus network structure during model selection
recovers complementary aspects of the neural activity pattern.
%
Equal region and network emphasis yields more dispersed,
less interpretable predictive model choices.
}
\label{fig_regnetratio}
\end{figure}

@@

\small
% \bibliographystyle{plainnat}
\bibliographystyle{splncs03}
\bibliography{paper_refs}

>>>>

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
% \usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
\usepackage[accepted]{icml2016}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Informing High-Dimensional Inference in Neuroimaging}

@@

\twocolumn[
\icmltitle{Region-Network Hierarchical Sparsity Priors for\\
High-Dimensional Inference in Brain Imaging}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2016
% package.
\icmlauthor{Danilo Bzdok}{danilo.bzdok@inria.fr}
\icmladdress{Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen, Germany\\
  Parietal, INRIA, NeuroSpin, bat 145, CEA, 91191 Gif-sur-Yvette France}
\icmlauthor{Michael Eickenberg}{Michael.Eickenberg@inria.fr}
\icmladdress{Department d'Informatique, Ecole Normale Superieure, Paris}
\icmlauthor{Ga\"el Varoquaux}{gael.varoquaux@inria.fr}
\icmlauthor{Bertrand Thirion}{bertrand.thirion@inria.fr}
\icmladdress{Parietal, INRIA, NeuroSpin, bat 145, CEA, 91191 Gif-sur-Yvette France}

% You may provide any keywords that you 
% find helpful for describing your paper; these are used to populate 
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Sparsity-inducing norms, hierarchical tree sparsity,
numerical optimization,
systems neuroscience,
functional specialization, functional integration}

@@

@@

\begin{table*}[h]
  \resizebox{0.98\textwidth}{!}{%
  \begin{tabular}{l|l|l}
    \hline
  {\bf Cognitive Task} & {\bf Stimuli}                         & {\bf Instruction for participants}                                                \\ \hline
  1 Reward             & \multirow{2}{*}{Card game}            & \multirow{2}{*}{Guess the number of a mystery card for gain/loss of money}        \\ \cline{1-1}
  2 Punish             &                                       &                                                                                   \\ \hline
  3 Shapes             & Shape pictures                        & Decide which of two shapes matches another shape geometrically                    \\ \hline
  4 Faces              & Face pictures                         & Decide which of two faces matches another face emotionally                        \\ \hline
  5 Random             & \multirow{2}{*}{Videos with objects}  & \multirow{2}{*}{Decide whether the objects act randomly or intentionally} \\ \cline{1-1}
  6 Theory of mind     &                                       &                                                                                   \\ \hline
  7 Mathematics        & Spoken numbers                        & Complete addition and subtraction problems                                        \\ \hline
  8 Language           & Auditory stories                      & Choose answer about the topic of the story                                        \\ \hline
  9 Tongue movement    & \multirow{3}{*}{Visual cues}          & Move tongue                                                                       \\ \cline{1-1} \cline{3-3} 
  10 Food movement     &                                       & Squeezing of the left or right toe                                                \\ \cline{1-1} \cline{3-3} 
  11 Hand movement     &                                       & Tapping of the left or right finger                                               \\ \hline
  12 Matching          & \multirow{2}{*}{Shapes with textures} & Decide whether two objects match in shape or texture                             \\ \cline{1-1} \cline{3-3} 
  13 Relations         &                                       & Decide whether object pairs differ both along either shape or texture             \\ \hline
  14 View Bodies       & Pictures                              & Passive watching                                                                   \\ \hline
  15 View Faces        & Pictures                              & Passive watching                                                                   \\ \hline
  16 View Places       & Pictures                              & Passive watching                                                                   \\ \hline
  17 View Tools        & Pictures                              & Passive watching                                                                   \\ \hline
  18 Two-Back          & Various pictures                      & Indicate whether current stimulus is the same as two items earlier                \\ \hline
  \end{tabular}
}
\vspace{-0.2cm}
\caption{\textbf{Description of psychological tasks to predict.}}
\label{table_tasks}
\end{table*}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=1.00\textwidth]{../figures/reg_net_prior_colin.pdf}
\end{centering}
\vspace{-0.6cm}
\caption{\textbf{Building blocks of the region-network tree.}
Depicts neurobiological priors introduced into the classification problem 
by hierarchical structured sparsity.
\textit{Left:} Continuous, partially overlapping brain network priors
(\textit{hot-colored}, taken from \cite{smith2009})
accommodate the functional integration
perspective of brain organization.
\textit{Right:} Discrete, non-overlapping brain region priors
(\textit{single-colored}, taken from \cite{crad12})
accommodate the functional segregation perspective.
\textit{Middle:} These two types of predefined voxel groups are incorporated
into hierarchical priors of parent networks with their
descending region nodes.
\textit{Top to bottom:} Four examplary region-network priors
are shown, including
the early cortex that processes
visual and sound information from the environment,
a well-known attentional circuit in the left brain hemisphere,
and
the cerebellum that is involved in motor behavior.
}
\label{fig_priors}
\end{figure*}

\begin{figure*}
\begin{centering}
\includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
\end{centering}
\vspace{-0.6cm}
\caption{\textbf{Model performance across sparsity priors.}
Compares the performance of logistic regression estimators
with 4 different structured and unstructered sparsity terms
in classifying neural activity from 18 psychological tasks.
The class-wise precision and recall metrics
were obtained on the same test set.
%
Unstructured $\ell_1$-penalized logistic regression (\textit{upper left})
imposed a minimum of relevant brain voxels without
assuming special structure.
Structured $\ell_1/\ell_2$-block norm with additional $\ell_1$ term
(\textit{lower left})
imposed region compartments, but naive to network structure.
Structured trace-norm penalization (\textit{lower right})
imposed low-rank structure
with sparsity of network patterns, but naive to region structure.
Structured $\ell_1/\ell_2$-block-norm with a hierarchy of
both region and network priors (\textit{upper right})
exhibited the best out-of-sample performance.
%
A priori knowledge of both region and network neighborhoods
was hence most beneficial for predicting psychological tasks from
brain maps.
}
\label{fig_sparsities}
\end{figure*}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
%\vspace{-0.6cm}
\caption{\textbf{Naive versus informed sparse model selection
across training set sizes.}
Ordinary $\ell_1$-penalized logistic regression
(\textit{upper row})
is compared
to hierarchical-tree-penalized logistic regression
(\textit{lower row})
with increasing fraction
of the available training data (\textit{left to right columns}).
For one example (i.e., ``View tools'') from 18 psychological tasks,
unthresholded axial maps of model weights
are shown for comparison against
the sample average of that class
(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
The out-of-sample accuracies for predicting all 18 psychological tasks
is given in percent.
%
In the data-scarce scenario,
typical for brain imaging,
hierarchical tree sparsity achieves much
better support recovery with the biggest difference
in model performance.
%
In the data-rich scenario,
neurobiologically informed logistic regression
profits more from the available information quantities than
neurobiologically naive logistic regression.
}
\label{fig_dataratio}
\end{centering}
\end{figure*}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=0.80\textwidth]{../figures/reg_net_ratio_colin.pdf}
%\vspace{-0.6cm}
\caption{\textbf{Support recovery as a function of
region and network emphasis.}
The relative impact of the region and network priors
on model selection
is systematically varied against each other.
This region-network ratio (\textit{upper fractions}) weighted voxel groups
to priviledge sparse models in function space
that acknowledge known brain region neighborhoods
(\textit{left columns}) or
known brain networks neighborhoods
(\textit{right columns}).
Among the 18 classes, the model weights are shown for the psychological
tasks (\textit{from top to bottom}): tongue movement, listening stories,
taking somebody else's perspective (ToM, "theory of mind"),
as well as
viewing locations and tools.
The 18-class out-of-sample accuracy is indicated
on the \textit{bottom} and
the class-wise mean neural activty
(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
%
Different emphasis on regions versus networks
in hierarchical structured sparsity can
yield comparable model performance.
%
Favoring region versus network structure during model selection
recovers complementary aspects of the neural activity pattern.
%
Equal region and network emphasis yields more dispersed,
less interpretable predictive model choices.
}
\label{fig_regnetratio}
\end{centering}
\end{figure*}

@@

\small
% \bibliographystyle{plainnat}
\bibliographystyle{icml2016}
\bibliography{paper_refs}
% \bibliography{paper_refs}
